# 1 Libraries

```{r libraries}
library(fistools)
library(camtrapdp)
library(tidyverse)
```

# 2 Input
These are the only values you should change:
- year: An integer specifying the year of interest
- serie: An integer sequence of the deployment series of interest
- species: A character or list of characters specifying the scientific names of
interest, example: c("Capreolus capreolus", "Sus scrofa", "Vulpes vulpes", "Dama dama")

```{r parameters}
years <- 2025
series <- 8:11
species <- c("Sus scrofa","Capreolus capreolus", "Vulpes vulpes")
```

```{r get data from drive}
zip_dir <- "./GMU8/Input"
files_dir <- "./GMU8/Input/FilesGMU8"

download_gdrive_if_missing(gfileID = "1U7cSwhUZRJlR_zpJvYyhsi24J2QV8U8q",
                           destfile = file.path(zip_dir, "gmu8.zip"),
                           update_always = TRUE,
                           email = Sys.getenv("email"))
# Note to student: you do not have the necessary rights to *make changes* in the Drive where this file is kept -- but you should have enough rights to access the file
# But no worries, if you need the latest export: ask anyone that works on the project to make a new export (make take a while) and update it in this Drive.
# It is essential that the new export be named gmu8.zip so that it replaces the old files, but keeps the same gfileID
unzip("./GMU8/Input/gmu8.zip",
      exdir = file.path(files_dir))
```

```{r read the datapackage}
gmu8 <- read_camtrapdp("./GMU8/Input/FilesGMU8/datapackage.json")
```

```{r unlink files & remove files}
unlink("./GMU8/Input/FilesGMU8",
       recursive = TRUE)
file.remove("./GMU8/Input/gmu8.zip")
```

# 3 Get relevant deployments

```{r filter deployments}
gmu8$data$deployments <- gmu8$data$deployments %>% 
  mutate(var = locationName) %>%
  separate(var, 
           into = c("year_loc",
                    "serie",
                    "gridcell"),
           "_") %>%
  mutate(year = year(deploymentStart)) 

pkg <- gmu8 |> 
  filter_deployments(serie %in% series) |> 
  filter_deployments(year %in% years)

table(pkg$data$deployment$serie, 
      pkg$data$deployment$year, useNA = "ifany")
table(pkg$data$observations$scientificName, useNA = "ifany")
table(pkg$data$observations$cameraSetupType, useNA = "ifany")
```

## 3.3 Filter for deployments with actual calibration within timeframe

```{r get deps with calibration}
calibration_deps <- pkg %>%
  filter_observations(cameraSetupType == "calibration") 

obs_list <- calibration_deps$data$observations
dep_list <- unique(obs_list$deploymentID)

data <- gmu8 |> 
  filter_deployments(deploymentID %in% dep_list)

track_data <- data %>% 
  filter_observations(scientificName %in% species)

table(track_data$data$observations$scientificName, useNA = "ifany")
table(track_data$data$observations$cameraSetupType, useNA = "ifany")
table(track_data$data$deployments$serie, useNA = "ifany")
```
# 4 Get relevant sequences
## 4.2. Combine all filters

```{r get relevant seqID}

seqID <- unique(track_data$data$observations$eventID) # All seq that have to be done at some point in time
```

# 5 Remove already-done sequences

```{r read seq_done}
seq_done <- read_csv("./GMU8/Input/tracking_seq_done.csv")
seq_done <- c(seq_done$sequenceID)
```

```{r rerun non-tracked listed as done}
non_tracked <- track_data |> 
  filter_observations(is.na(individualSpeed) & observationLevel == "event")

tracked <- track_data |> 
  filter_observations(!is.na(individualSpeed) & observationLevel == "event")

non_tracked_seq <- unique(non_tracked$data$observations$eventID)
tracked_seq <- unique(tracked$data$observations$eventID)

non_tracked_seq <- non_tracked_seq[!non_tracked_seq %in% 
                                     tracked_seq]

# Sometimes the sequence is tracked but the speed could not be calculated
# This occurs in 3 known cases, namely:
# 1. An error occured while parsing the data => These should be reported to Yorick
non_tracked_parsing_error <- non_tracked$data$observations |> 
  filter(grepl(pattern = "Error parsing all data",
               x = observationComments)) |> 
  write_csv("./GMU8/Interim/non_tracked_parsing_error.csv")

non_tracked_seq <- non_tracked_seq[!non_tracked_seq %in% 
                                     non_tracked_parsing_error$eventID]

# 2. Not enough poles were available to do the calibration. These should be 
# revisited via another way. 
non_tracked_toofew_poles <- non_tracked$data$observations |> 
  filter(grepl(pattern = "Not enough poles calibrated, minimum is 6",
               x = observationComments))|> 
  write_csv("./GMU8/Interim/non_tracked_toofew_poles.csv")

non_tracked_seq <- non_tracked_seq[!non_tracked_seq %in% 
                                     non_tracked_toofew_poles$eventID]

# 3. Not enough positions were logged to calculate the speed => These should be 
# revisited via this script.
non_tracked_toofew_positions <- non_tracked$data$observations |> 
  filter(grepl(pattern = "Not enough positions for speed and distance",
               x = observationComments))|> 
  write_csv("./GMU8/Interim/non_tracked_toofew_positions.csv")

if(nrow(non_tracked_toofew_positions) > 0){
  redo_toofew_positions <- askYesNo(msg = paste(nrow(non_tracked_toofew_positions), 
                                                "sequenties with too few positions detected, redo?"))
  if(!redo_toofew_positions){
    non_tracked_seq <- non_tracked_seq[!non_tracked_seq %in% 
                                         non_tracked_toofew_positions$eventID]
  }
}

non_tracked_done <- unique(seq_done[seq_done %in% non_tracked_seq])

if(length(non_tracked_done) > 0){
  cat(length(non_tracked_done), "Non-tracked sequences detected on the sequences 
      done list => asking rerun")
  
  redo_non_tracked <- askYesNo("Do you want to redo the non-tracked sequences ?")
  
  if(redo_non_tracked){
    
    seq_done <- seq_done[!seq_done %in% non_tracked_seq]
    
    seq_done |> 
      as.data.frame() |> 
      rename("sequenceID" = 1) |> 
      write_csv("./GMU8/Input/tracking_seq_done.csv")
  }
}
```

```{r filter out seq_done}
seqID <- seqID[!seqID %in% seq_done]
```

# 6 Open sequences in Agouti

Before you run this, read this:

This for-loop will open the relevant sequences one-by-one in Agouti. To ensure you don't get flooded by all the sequences at once, I built in a break by means of a popu-up. This is what the different options mean:

* YES/JA: I have tracked this sequence and I want to go to the next sequence
* NO/NEE: I have tracked this sequence but I need a break (for whatever reason), so do not open the next sequence in Agouti
* CANCEL/ANNULEREN: I have not annotated this sequence (for whaterver reason) and do not want to see the next sequence. *WARNING Check that this last sequenceID is not added to tracking_seq_done.csv. If yes, delete this (and ONLY this) seqID manually from tracking_seq_done.csv*

```{r open leftover seq in Agouti}
project_id <- "91e1e104-a296-461e-af79-eeb6cb3e6c7f"

for (i in 1:length(seqID)) {
  # Open URL
  browseURL(url = paste0("https://www.agouti.eu/project/", 
                         project_id, 
                         "/annotate/sequence/",
                         seqID[i]))
  
  # Next sequence?
  next_seq <- askYesNo("Do you wanna go to the next sequence?")
  
  if(is.na(next_seq)){
    break
  }
  
  if (next_seq) {
    # append seqID to done file to skip next time
    write.table(data.frame(sequenceID = seqID[i]),
                "./GMU8/Input/tracking_seq_done.csv",  # Make sure these are in your WD
                append = TRUE,
                row.names = FALSE,
                col.names = FALSE)
  }else{
    # append seqID to done file to skip next time
    write.table(data.frame(sequenceID = seqID[i]),
                "./GMU8/Input/tracking_seq_done.csv",  # Make sure these are in your WD
                append = TRUE,
                row.names = FALSE,
                col.names = FALSE)
    break
  }
}
```

