# 1 Libraries
```{r install fistools dev version, eval = FALSE}
remotes::install_github("inbo/fistools@170-new-function-redo_non_tracked")
```

```{r libraries}
library(fistools)
library(camtrapdp)
library(tidyverse)
```

# 2 Input
These are the only values you should change:
- year: An integer specifying the year of interest
- serie: An integer sequence of the deployment series of interest
- species: A character or list of characters specifying the scientific names of
interest, example: c("Capreolus capreolus", "Sus scrofa", "Vulpes vulpes", "Dama dama")

```{r parameters}
years <- 2025
series <- 8:11
species <- c("Sus scrofa","Capreolus capreolus", "Vulpes vulpes")
```

```{r get data from drive}
zip_dir <- "./GMU8/Input"
files_dir <- "./GMU8/Input/FilesGMU8"

download_gdrive_if_missing(gfileID = "1U7cSwhUZRJlR_zpJvYyhsi24J2QV8U8q",
                           destfile = file.path(zip_dir, "gmu8.zip"),
                           update_always = TRUE,
                           email = Sys.getenv("email"))
# Note to student: you do not have the necessary rights to *make changes* in the Drive where this file is kept -- but you should have enough rights to access the file
# But no worries, if you need the latest export: ask anyone that works on the project to make a new export (make take a while) and update it in this Drive.
# It is essential that the new export be named gmu8.zip so that it replaces the old files, but keeps the same gfileID
unzip("./GMU8/Input/gmu8.zip",
      exdir = file.path(files_dir))
```

```{r read the datapackage}
gmu8 <- read_camtrapdp("./GMU8/Input/FilesGMU8/datapackage.json")
```

```{r unlink files & remove files}
unlink("./GMU8/Input/FilesGMU8",
       recursive = TRUE)
file.remove("./GMU8/Input/gmu8.zip")
```

# 3 Get relevant deployments

```{r filter deployments}
gmu8$data$deployments <- gmu8$data$deployments %>% 
  mutate(var = locationName) %>%
  separate(var, 
           into = c("year_loc",
                    "serie",
                    "gridcell"),
           "_") %>%
  mutate(year = year(deploymentStart)) 

pkg <- gmu8 |> 
  filter_deployments(serie %in% series) |> 
  filter_deployments(year %in% years)

table(pkg$data$deployment$serie, 
      pkg$data$deployment$year, useNA = "ifany")
table(pkg$data$observations$scientificName, useNA = "ifany")
table(pkg$data$observations$cameraSetupType, useNA = "ifany")
```

## 3.3 Filter for deployments with actual calibration within timeframe

```{r get deps with calibration}
calibration_deps <- pkg %>%
  filter_observations(cameraSetupType == "calibration") 

obs_list <- calibration_deps$data$observations
dep_list <- unique(obs_list$deploymentID)

data <- gmu8 |> 
  filter_deployments(deploymentID %in% dep_list)

track_data <- data %>% 
  filter_observations(scientificName %in% species)

table(track_data$data$observations$scientificName, useNA = "ifany")
table(track_data$data$observations$cameraSetupType, useNA = "ifany")
table(track_data$data$deployments$serie, useNA = "ifany")
```
# 4 Get relevant sequences
## 4.2. Combine all filters

```{r get relevant seqID}
seqID <- unique(track_data$data$observations$eventID) # All seq that have to be done at some point in time
```

# 5 Remove already-done sequences

```{r read seq_done}
seq_done <- read_csv("./GMU8/Input/tracking_seq_done.csv")
seq_done <- c(seq_done$sequenceID)
```

```{r redo non tracked}
non_tracked <- redo_non_tracked(track_data = track_data,
                                seq_done_in = seq_done,
                                redo_non_tracked = FALSE,
                                redo_toofew_positions = FALSE,
                                add_tracked = TRUE)

seq_done <- non_tracked$seq_done_out |> 
  as.data.frame() |> 
  rename("sequenceID" = 1) |> 
  write_csv("./GMU8/Input/tracking_seq_done.csv")

seqID <- seqID[!seqID %in% seq_done$sequenceID]

non_tracked$non_tracked_toofew_poles |> 
  write_csv("./GMU8/Interim/non_tracked_toofew_poles.csv")
non_tracked$non_tracked_parsing_error |> 
  write_csv("./GMU8/Interim/non_tracked_parsing_error.csv")
non_tracked$non_tracked_other_issues |> 
  write_csv("./GMU8/Interim/non_tracked_other_issues.csv")
```

```{r filter out seq_done}
seqID <- seqID[!seqID %in% seq_done$sequenceID]
```

# 6 Open sequences in Agouti

Before you run this, read this:

This for-loop will open the relevant sequences one-by-one in Agouti. To ensure you don't get flooded by all the sequences at once, I built in a break by means of a popu-up. This is what the different options mean:

* YES/JA: I have tracked this sequence and I want to go to the next sequence
* NO/NEE: I have tracked this sequence but I need a break (for whatever reason), so do not open the next sequence in Agouti
* CANCEL/ANNULEREN: I have not annotated this sequence (for whaterver reason) and do not want to see the next sequence. *WARNING Check that this last sequenceID is not added to tracking_seq_done.csv. If yes, delete this (and ONLY this) seqID manually from tracking_seq_done.csv*

```{r open leftover seq in Agouti}
project_id <- "91e1e104-a296-461e-af79-eeb6cb3e6c7f"

for (i in 1:length(seqID)) {
  # Open URL
  browseURL(url = paste0("https://www.agouti.eu/project/", 
                         project_id, 
                         "/annotate/sequence/",
                         seqID[i]))
  
  # Next sequence?
  next_seq <- askYesNo("Do you wanna go to the next sequence?")
  
  if(is.na(next_seq)){
    break
  }
  
  if (next_seq) {
    # append seqID to done file to skip next time
    seq_done <- seq_done |> 
      as.data.frame() |> 
      add_row(sequenceID = seqID[i]) |> 
      write_csv("./GMU8/Input/tracking_seq_done.csv")
    
  }else{
    # append seqID to done file to skip next time
    seq_done <- seq_done |> 
      as.data.frame() |> 
      add_row(sequenceID = seqID[i]) |> 
      write_csv("./GMU8/Input/tracking_seq_done.csv")
    break
  }
}
```

