# 1 Libraries

```{r install fistools dev version, eval = FALSE}
remotes::install_github("inbo/fistools@170-new-function-redo_non_tracked")
```

```{r}
library(fistools)
library(camtrapdp)
library(tidyverse)
```

# 2 Input
These are the only values you should change:
- year: An integer specifying the year of interest
- serie: An integer sequence of the deployment series of interest
- species: A character or list of characters specifying the scientific names of
interest, example: c("Capreolus capreolus", "Sus scrofa", "Vulpes vulpes", "Dama dama")

```{r parameters}
years <- 2025
series <- 10:11
species <- c("Capreolus capreolus", "Dama dama", "Vulpes vulpes")
```

```{r get data from drive}
download_gdrive_if_missing(gfileID = "1F7mCj-Wm0Ggq1evz1HusxZBgX-1ttx-S",
                           destfile = "./Drongengoed/Input/drongengoed.zip", 
                           email = Sys.getenv("email"),
                           update_always = TRUE)
# Note to student: you do not have the necessary rights to *make changes* in the Drive where this file is kept -- but you should have enough rights to access the file
# But no worries, if you need the latest export: ask anyone that works on the project to make a new export (make take a while) and update it in this Drive.
# It is essential that the new export be named drongengoed.zip so that it replaces the old files, but keeps the same gfileID
```

```{r unzip and read data}
# Unzip data
unzip("./Drongengoed/Input/drongengoed.zip", 
      exdir = "./Drongengoed/Input/Files")

# Read data
drg <- read_camtrapdp("./Drongengoed/Input/Files/datapackage.json")
```

```{r unlink files}
unlink("./Drongengoed/Input/Files",
       recursive = TRUE)
file.remove("./Drongengoed/Input/drongengoed.zip")
```

# 3 Get relevant deployments

```{r}
drg$data$deployments <-  drg$data$deployments %>%
  mutate(year = year(deploymentStart),
         month = month(deploymentStart))

pkg <- drg |> 
  filter_deployments(month %in% series) |> 
  filter_deployments(year %in% years)

table(pkg$data$deployment$month, 
      pkg$data$deployment$year, useNA = "ifany")
table(pkg$data$observations$scientificName, useNA = "ifany")
table(pkg$data$observations$cameraSetupType, useNA = "ifany")
```

## 3.3 Filter for deployments with actual calibration within timeframe

```{r get deps with calibration}
calibration_deps <- pkg %>%
  filter_observations(cameraSetupType == "calibration") 

obs_list <- calibration_deps$data$observations
dep_list <- unique(obs_list$deploymentID)

data <- drg |> 
  filter_deployments(deploymentID %in% dep_list)

track_data <- data %>% 
  filter_observations(scientificName %in% species)

table(track_data$data$observations$scientificName, useNA = "ifany")
table(track_data$data$observations$cameraSetupType, useNA = "ifany")
table(track_data$data$deployments$month, useNA = "ifany")
```

# 4 Get relevant sequences

## 4.1 Species filter

## 4.2 Combine all filters

```{r}
seqID <- unique(track_data$data$observations$eventID)
```

# 5 Remove already-done sequences

IF YOU TOOK A BREAK FROM THE FOR-LOOP, RERUN CODE BELOW TO CONTINUE

```{r}
seq_done <- read_csv("./Drongengoed/Input/tracking_seq_done.csv")
n_unique<- n_distinct(seq_done$sequenceID)

seq_done <- c(seq_done$sequenceID)
```

```{r redo non tracked}
non_tracked <- redo_non_tracked(track_data = track_data,
                                seq_done_in = seq_done,
                                redo_non_tracked = FALSE,
                                redo_toofew_positions = FALSE,
                                add_tracked = TRUE)

seq_done <- non_tracked$seq_done_out |> 
  as.data.frame() |> 
  rename("sequenceID" = 1) |> 
  write_csv("./Drongengoed/Input/tracking_seq_done.csv")

seqID <- seqID[!seqID %in% seq_done]

non_tracked$non_tracked_toofew_poles |> 
  write_csv("./Drongengoed/Interim/non_tracked_toofew_poles.csv")
non_tracked$non_tracked_parsing_error |> 
  write_csv("./Drongengoed/Interim/non_tracked_parsing_error.csv")
non_tracked$non_tracked_other_issues |> 
  write_csv("./Drongengoed/Interim/non_tracked_other_issues.csv")
```

# 6 Open sequences in Agouti

Before you run this, read this:

This for-loop will open the relevant sequences one-by-one in Agouti. To ensure you don't get flooded by all the sequences at once, I built in a break by means of a popu-up. This is what the different options mean:

* YES/JA: I have tracked this sequence and I want to go to the next sequence
* NO/NEE: I have tracked this sequence but I need a break (for whatever reason), so do not open the next sequence in Agouti
* CANCEL/ANNULEREN: I have not annotated this sequence (for whaterver reason) and do not want to see the next sequence. *WARNING Check that this last sequenceID is not added to tracking_seq_done.csv. If yes, delete this (and ONLY this) seqID manually from tracking_seq_done.csv*

```{r}
project_id <- "e10e6b2b-78fc-44ad-9d66-c4d0b1dd889e"

for (i in 1:length(seqID)) {
  # Open URL
  browseURL(url = paste0("https://www.agouti.eu/project/", 
                         project_id, 
                         "/annotate/sequence/",
                         seqID[i]))
  # Next sequence?
  next_seq <- askYesNo("Do you wanna go to the next sequence?")
  
  if(is.na(next_seq)){
    break
  }
  
  if (next_seq) {
    # append seqID to done file to skip next time
    write.table(data.frame(sequenceID = seqID[i]),
                "./Drongengoed/Input/tracking_seq_done.csv",  # Make sure these are in your WD
                append = TRUE,
                row.names = FALSE,
                col.names = FALSE)
  }else{
    # append seqID to done file to skip next time
    write.table(data.frame(sequenceID = seqID[i]),
                "./Drongengoed/Input/tracking_seq_done.csv",  # Make sure these are in your WD
                append = TRUE,
                row.names = FALSE,
                col.names = FALSE)
    break
  }
}
```

